---
title: "Predictors of Depression During the Covid-19 Pandemic" 
subtitle: "K-Medoids Clustering part 2: Cluster Visuals"
author: "Sarka Tesarova, Ondrej Pekacek, Alessandro Porrovecchio"
date: "Last edited `r format (Sys.time(),'%d. %m. %Y')`"
output:
  html_document: 
    number_sections: true
    theme: readable
    code_folding: hide
    code_download: true
    css: docs/style.css
    includes:
      in_header: docs/header.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r include=FALSE}
# Package names
packages <- c("dplyr", "tidyr", "NbClust", "factoextra", "cluster", "clValid", "mice", "plotly", "viridis", "fpc", "tibble", "Rtsne", "DT", "crosstalk")

# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# Packages loading
invisible(lapply(packages, library, character.only = TRUE))
```

```{r include=FALSE}
clust_eval_stats <- readRDS("data/clust_eval_stats.rds")
clust_tsne_data <- readRDS("data/clust_tsne_data.rds")
list_cl_dfs <- readRDS("data/list_clustered_dfs.rds") 
list_cl_dfs <- lapply(list_cl_dfs, function(x) x$pooled)

for (i in seq_along(list_cl_dfs)) { list_cl_dfs[[i]][["cluster"]] <- as.factor(list_cl_dfs[[i]][["cluster"]])}
                           
compare_cluster_validation <- do.call(rbind, lapply(clust_eval_stats, function(x) x$pooled)) %>% rownames_to_column(var = "cluster_size")

clust_tsne_data_long <- lapply(clust_tsne_data, function(x) x$pooled) %>% bind_rows(.id = "cluster_config") %>% mutate(cluster = as.factor(cluster), cluster_config = factor(cluster_config, levels = c(paste0("clusters_", 2:15))))
```

# Cluster validation statistics for different cluster sizes {.tabset .tabset-pills}

```{r include=FALSE}
sd <- SharedData$new(compare_cluster_validation, key = ~cluster_size)

interactive_table <- datatable(sd, height = "100%",
        options = list(
        dom = "t",
        pageLength = 20,
    initComplete = JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#4C535D', 'color': '#fff'});",
    "}")
)) %>%
  formatRound(c("dunn_2", "silhouette_wdt", "widest_gap", "pearson_gamma", "sep_index", "avg_within", "avg_between"), 3) %>% 
  formatRound(c("dunn_1"), 4) %>%
  formatRound(c("ch_index"), 0) %>%
  formatStyle("cluster_size", fontWeight = "bold")

clust_tsne_data_long <- lapply(clust_tsne_data, function(x) x$pooled) %>% bind_rows(.id = "cluster_config") %>% mutate(cluster = as.factor(cluster), cluster_config = factor(cluster_config, levels = c(paste0("clusters_", 2:15))))
```

## Dunn index 1 (higher better)
	

```{r}
bscols(
  widths = c(8, 4),
  interactive_table, plot_ly(sd, x = ~cluster_size, y = ~dunn_1, type = "bar"), device = "lg"
)
```

---

## Dunn index 2 (higher better)

```{r}
bscols(
  widths = c(8, 4),
  interactive_table, plot_ly(sd, x = ~cluster_size, y = ~dunn_2, type = "bar"), device = "lg"
)
```

---

## Average Silhoutte Width (higher better)

```{r}
bscols(
  widths = c(8, 4),
  interactive_table, plot_ly(sd, x = ~cluster_size, y = ~silhouette_wdt, type = "bar"), device = "lg"
)
```

---

## Pearson Gamma (higher better)

```{r}
bscols(
  widths = c(8, 4),
  interactive_table, plot_ly(sd, x = ~cluster_size, y = ~pearson_gamma, type = "bar"), device = "lg"
)
```

---

## Separation Index (higher better)

```{r}
bscols(
  widths = c(8, 4),
  interactive_table, plot_ly(sd, x = ~cluster_size, y = ~sep_index, type = "bar"), device = "lg"
)
```

---

## Calinski & Harabasz index (higher better)

```{r}
bscols(
  widths = c(8, 4),
  interactive_table, plot_ly(sd, x = ~cluster_size, y = ~ch_index, type = "bar"), device = "lg"
)
```

---

## Avg. distance within clusters (higher better)

```{r}
bscols(
  widths = c(8, 4),
  interactive_table, plot_ly(sd, x = ~cluster_size, y = ~avg_within, type = "bar"), device = "lg"
)
```

---

## Avg. distance between clusters (higher better)

```{r}
bscols(
  widths = c(8, 4),
  interactive_table, plot_ly(sd, x = ~cluster_size, y = ~avg_between, type = "bar"), device = "lg"
)
```

---

## Widest within-cluster gap (lower better)

```{r}
bscols(
  widths = c(8, 4),
  interactive_table, plot_ly(sd, x = ~cluster_size, y = ~widest_gap, type = "bar"), device = "lg"
)

```

---

# t-SNE Visualization for different cluster sizes

```{r fig.height=20, fig.width=20}

# t-Distributed Stochastic Neighbor Embedding visualization
  ggplot(aes(x = X, y = Y), data = clust_tsne_data_long) +
    geom_point(aes(color = cluster)) + 
    # scale_color_viridis(discrete = TRUE) +
    facet_wrap(~ cluster_config)
```

---

# Interpretation of clusters using relative values for each variable {.tabset .tabset-pills}

## 2 clusters
```{r fig.height=12, fig.width=20}
# Cluster visualization for k clusters
(ggplot(list_cl_dfs$clusters_2, aes(x = variable, y = value, group = cluster, colour = cluster)) +
  stat_summary(geom = "point",
               fun = mean,
               size = 3) +
  stat_summary(geom = "line", fun = mean) +
  scale_color_viridis(discrete = TRUE) +
  ggtitle("Average value of selected variables per cluster") +
  theme_bw() +
  ylab("relative value")) %>% ggplotly()

```

## 3 clusters
```{r fig.height=12, fig.width=20}
# Cluster visualization for k clusters
(ggplot(list_cl_dfs$clusters_3, aes(x = variable, y = value, group = cluster, colour = cluster)) +
  stat_summary(geom = "point",
               fun = mean,
               size = 3) +
  stat_summary(geom = "line", fun = mean) +
  scale_color_viridis(discrete = TRUE) +
  ggtitle("Average value of selected variables per cluster") +
  theme_bw() +
  ylab("relative value")) %>% ggplotly()

```

## 4 clusters
```{r fig.height=12, fig.width=20}
# Cluster visualization for k clusters
(ggplot(list_cl_dfs$clusters_4, aes(x = variable, y = value, group = cluster, colour = cluster)) +
  stat_summary(geom = "point",
               fun = mean,
               size = 3) +
  stat_summary(geom = "line", fun = mean) +
  scale_color_viridis(discrete = TRUE) +
  ggtitle("Average value of selected variables per cluster") +
  theme_bw() +
  ylab("relative value")) %>% ggplotly()

```

## 5 clusters
```{r fig.height=12, fig.width=20}
# Cluster visualization for k clusters
(ggplot(list_cl_dfs$clusters_5, aes(x = variable, y = value, group = cluster, colour = cluster)) +
  stat_summary(geom = "point",
               fun = mean,
               size = 3) +
  stat_summary(geom = "line", fun = mean) +
  scale_color_viridis(discrete = TRUE) +
  ggtitle("Average value of selected variables per cluster") +
  theme_bw() +
  ylab("relative value")) %>% ggplotly()

```

## 6 clusters
```{r fig.height=12, fig.width=20}
# Cluster visualization for k clusters
(ggplot(list_cl_dfs$clusters_6, aes(x = variable, y = value, group = cluster, colour = cluster)) +
  stat_summary(geom = "point",
               fun = mean,
               size = 3) +
  stat_summary(geom = "line", fun = mean) +
  scale_color_viridis(discrete = TRUE) +
  ggtitle("Average value of selected variables per cluster") +
  theme_bw() +
  ylab("relative value")) %>% ggplotly()

```

## 7 clusters
```{r fig.height=12, fig.width=20}
# Cluster visualization for k clusters
(ggplot(list_cl_dfs$clusters_7, aes(x = variable, y = value, group = cluster, colour = cluster)) +
  stat_summary(geom = "point",
               fun = mean,
               size = 3) +
  stat_summary(geom = "line", fun = mean) +
  scale_color_viridis(discrete = TRUE) +
  ggtitle("Average value of selected variables per cluster") +
  theme_bw() +
  ylab("relative value")) %>% ggplotly()

```

## 8 clusters
```{r fig.height=12, fig.width=20}
# Cluster visualization for k clusters
(ggplot(list_cl_dfs$clusters_8, aes(x = variable, y = value, group = cluster, colour = cluster)) +
  stat_summary(geom = "point",
               fun = mean,
               size = 3) +
  stat_summary(geom = "line", fun = mean) +
  scale_color_viridis(discrete = TRUE) +
  ggtitle("Average value of selected variables per cluster") +
  theme_bw() +
  ylab("relative value")) %>% ggplotly()

```

## 9 clusters
```{r fig.height=12, fig.width=20}
# Cluster visualization for k clusters
(ggplot(list_cl_dfs$clusters_9, aes(x = variable, y = value, group = cluster, colour = cluster)) +
  stat_summary(geom = "point",
               fun = mean,
               size = 3) +
  stat_summary(geom = "line", fun = mean) +
  scale_color_viridis(discrete = TRUE) +
  ggtitle("Average value of selected variables per cluster") +
  theme_bw() +
  ylab("relative value")) %>% ggplotly()

```

## 10 clusters
```{r fig.height=12, fig.width=20}
# Cluster visualization for k clusters
(ggplot(list_cl_dfs$clusters_10, aes(x = variable, y = value, group = cluster, colour = cluster)) +
  stat_summary(geom = "point",
               fun = mean,
               size = 3) +
  stat_summary(geom = "line", fun = mean) +
  scale_color_viridis(discrete = TRUE) +
  ggtitle("Average value of selected variables per cluster") +
  theme_bw() +
  ylab("relative value")) %>% ggplotly()

```

## 11 clusters
```{r fig.height=12, fig.width=20}
# Cluster visualization for k clusters
(ggplot(list_cl_dfs$clusters_11, aes(x = variable, y = value, group = cluster, colour = cluster)) +
  stat_summary(geom = "point",
               fun = mean,
               size = 3) +
  stat_summary(geom = "line", fun = mean) +
  scale_color_viridis(discrete = TRUE) +
  ggtitle("Average value of selected variables per cluster") +
  theme_bw() +
  ylab("relative value")) %>% ggplotly()

```

## 12 clusters
```{r fig.height=12, fig.width=20}
# Cluster visualization for k clusters
(ggplot(list_cl_dfs$clusters_12, aes(x = variable, y = value, group = cluster, colour = cluster)) +
  stat_summary(geom = "point",
               fun = mean,
               size = 3) +
  stat_summary(geom = "line", fun = mean) +
  scale_color_viridis(discrete = TRUE) +
  ggtitle("Average value of selected variables per cluster") +
  theme_bw() +
  ylab("relative value")) %>% ggplotly()

```

## 13 clusters
```{r fig.height=12, fig.width=20}
# Cluster visualization for k clusters
(ggplot(list_cl_dfs$clusters_13, aes(x = variable, y = value, group = cluster, colour = cluster)) +
  stat_summary(geom = "point",
               fun = mean,
               size = 3) +
  stat_summary(geom = "line", fun = mean) +
  scale_color_viridis(discrete = TRUE) +
  ggtitle("Average value of selected variables per cluster") +
  theme_bw() +
  ylab("relative value")) %>% ggplotly()

```

## 14 clusters
```{r fig.height=12, fig.width=20}
# Cluster visualization for k clusters
(ggplot(list_cl_dfs$clusters_14, aes(x = variable, y = value, group = cluster, colour = cluster)) +
  stat_summary(geom = "point",
               fun = mean,
               size = 3) +
  stat_summary(geom = "line", fun = mean) +
  scale_color_viridis(discrete = TRUE) +
  ggtitle("Average value of selected variables per cluster") +
  theme_bw() +
  ylab("relative value")) %>% ggplotly()

```

## 15 clusters
```{r fig.height=12, fig.width=20}
# Cluster visualization for k clusters
(ggplot(list_cl_dfs$clusters_15, aes(x = variable, y = value, group = cluster, colour = cluster)) +
  stat_summary(geom = "point",
               fun = mean,
               size = 3) +
  stat_summary(geom = "line", fun = mean) +
  scale_color_viridis(discrete = TRUE) +
  ggtitle("Average value of selected variables per cluster") +
  theme_bw() +
  ylab("relative value")) %>% ggplotly()

```





